Summary Tables

### 2019-04-25 summary_tables.Rmd
Added PA summary tables

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person")))
    cat("\n")
}

>>>>

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)

    count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))
    cat("\n")
}

## Physical activity tables
Case study specific physical activity tables for backgound (non-travel) PA, and baseline and five scenarios (non-travel + travel)

```{r mmets = "asis"}

for(city in cities){
  df1 <- as.data.frame(io[[city]]$synth_pop$work_ltpa_marg_met)
  colnames(df1) <- "mmet"

  td1 <- df1 %>% filter(mmet == 0) %>% 
    summarise(perct_zeros = round(n() / nrow(df1) * 100, 1))

  td2 <- df1 %>%
    summarise(min = min(mmet),
              q_25th = round(quantile(mmet, 0.25), 1),
              median = round(quantile(mmet, 0.50), 1),
              mean = round(mean(mmet), 1),
              q_75th = round(quantile(mmet, 0.75), 1),
              q_90th = round(quantile(mmet, 0.95), 1),
              max = round(max(mmet), 1))

  td3 <- cbind(td1, td2)
  td3 <- as.data.frame(t(td3))

  df2 <- select(io[[city]]$outcomes$mmets, base_mmet : scen5_mmet)

  td4 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    filter(mmet == 0) %>% 
    group_by(scenario) %>% 
    summarise(perct_zeros = round(n() / nrow(df2) * 100, 1))

  td5 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    group_by(scenario) %>% 
    summarise(min = min(mmet),
              q_25th = round(quantile(mmet, 0.25), 1),
              median = round(quantile(mmet, 0.50), 1),
              mean = round(mean(mmet), 1),
              q_75th = round(quantile(mmet, 0.75), 1),
              q_90th = round(quantile(mmet, 0.95), 1),
              max = round(max(mmet), 1))

  td6 <- left_join(td4, td5, "scenario")
  td6 <- as.data.frame(t(td6))
  td6 <- td6[-1,]
  td6 <- mutate_all(td6, function(x) as.numeric(as.character(x)))

  td <- cbind(td3, td6)

  colnames(td)[1] <- "Background (non-travel)"
  colnames(td)[2] <- "Baseline"
  colnames(td)[3:7] <- rownames(scen_prop)

  print(kable(td, caption = paste("Marginal MET-h/wk for ", city)))
  cat("\n")
}
